Networked Character Devices

### 2011-12-08 report/presentation.tex
presentation: setup themes, cleanup
presentation: high level arch

\documentclass[xcolor=dvipsnames]{beamer}
%\useoutertheme{default}
%\usetheme{Boadilla}
\setbeamercovered{transparent=25}
\setbeamertemplate{blocks}[rounded][shadow=false] 
\setbeamertemplate{navigation symbols}{}

@@

\title[NCD]{Networked Character Devices}
%\subtitle[]{}
\author[ M. Monaco \& A. Sayler \& L Spear]{Matthew Monaco \&
                                            Andy Sayler \&
                                            Landon Spear}
\institute[University of Colorado]{
  University of Colorado\\
  \texttt{matthew.monaco@colorado.edu}\\*
  \texttt{andrew.sayler@colorado.edu}\\*
  \texttt{landon.spear@colorado.edu}
}
\date[Dec. 10, 2011]{Saturday, December 10\textsuperscript{th}, 2011}

@@

@@

\section{System}

@@

% Andy - End

@@

>>>>

\documentclass[xcolor=dvipsnames]{beamer}
\usetheme{AnnArbor}
\usecolortheme{beaver}
\setbeamercovered{transparent=25}
\setbeamertemplate{blocks}[rounded][shadow=false] 
\setbeamertemplate{navigation symbols}{}

@@

\title[NCD]{Networked Character Devices}
%\subtitle[]{}
\author[Monaco, Sayler, Spear]{Matthew Monaco \&
                               Andy Sayler \&
                               Landon Spear}
\institute[CU-Boulder]{
  University of Colorado at Boulder \\
  \texttt{\{first.last\}@colorado.edu}
}
\date[Dec. 10, 2011]{Saturday, December 10\textsuperscript{th}, 2011}

@@

\begin{frame}{Outline}
  \tableofcontents
\end{frame}

@@

\begin{frame}[c]{Very High Level}
  \includegraphics[width=0.8\textwidth]{arch-01.png}

  Our system uses a basic client server model
\end{frame}

@@

% Matt - End

@@

% vim: set sw=2 ts=2 et : %
